### 2023-11-12 ms.qmd
Changes analyses

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest)

@@

# Load data
	data  <-  read.csv("./data/.csv")
```

```{r, dataclean}
#| label: dataclean
#| echo: false
#| warning: false

# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
data_associative <- data %>%
  group_by(lizard_id) %>%
    filter(sum(is.na(FC_associative)) <= 15) %>%
    filter(trial_associative <= 35) %>%
  ungroup()  %>% 
    mutate(temp = gsub("[AB]_", "", trt),
          cort = gsub("_[2][38]", "", trt))  %>% 
    mutate(group = factor(group, levels = c("R_B", "B_R"))) %>%
  data.frame()

# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)

data_associative <- data_associative %>%
  group_by(lizard_id) %>%
  mutate(
    first_non_na = min(which(!is.na(FC_associative))),
    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
    filter(Associative_Trial >= 1) %>%
   ungroup() %>% data.frame()

write.csv(data_associative, file= "./output/Checking/data_associative.csv")

# Split data by species
deli_associative <- data_associative %>% filter (species == "delicata")
guich_associative <- data_associative %>% filter (species == "guichenoti")

>>>>

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, MASS)

@@

# Load data
	data  <-  read.csv("./data/Stressor.csv")
```

```{r, dataexplore}
#| label: dataexplore
#| echo: false
#| warning: false

# Divide Treatment in CORT and Temperature
data <- data %>%
      mutate(temp = gsub("[AB]_", "", trt),
          cort = gsub("_[2][38]", "", trt))  %>% 
  data.frame()

# Transform mass into mg
data$mass <- data$mass*1000

# Split data by species
deli_stressor <- data %>% filter (species == "delicata")
guich_stressor <- data %>% filter (species == "guichenoti")

# Explore distributions of variables

# A) L. deli
    #a.1) Mass 
plot_mass <- ggplot(deli_stressor, aes(x = mass, fill = interaction(as.factor(temp),as.factor(cort), sep="_"))) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 30, color = "black") +
  scale_fill_manual(values = c("28_A" = "red", "23_A" = "blue", "28_B" = "salmon", "23_B" = "lightblue")) +
  labs(x = "Mass", y = "Density", fill = "Temperature ~ CORT") +
  theme_minimal() +
  facet_grid(cort*temp~Day, scales = "free_y")
print(plot_mass)

    #a.2) Latency to move
plot_freeze <- ggplot(deli_stressor, aes(x = log(lat_to_move+1), fill = interaction(as.factor(temp),as.factor(cort), sep="_"))) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 30, color = "black") +
  scale_fill_manual(values = c("28_A" = "red", "23_A" = "blue", "28_B" = "salmon", "23_B" = "lightblue")) +
  labs(x = "Mass", y = "Density", fill = "Temperature ~ CORT") +
  theme_minimal() +
  facet_grid(cort*temp~Day, scales = "free_y")
print(plot_freeze)

# I will both distributions with saphiro.test and lat_to_move with a qqplot
mass_normal_test<-by(deli_stressor$mass, interaction (deli_stressor$cort, deli_stressor$temp, deli_stressor$Day), function(x) shapiro.test((x)))
print(mass_normal_test)

freeze_normal_test<-by(deli_stressor$lat_to_move, interaction (deli_stressor$cort, deli_stressor$temp, deli_stressor$Day), function(x) shapiro.test(log(x+1)))
print(freeze_normal_test)
# Once checked the distributions, I will transform lat_to_move with log(x+1) to make it normal

# B) L. guich
    #b.1) Mass 
plot_mass <- ggplot(guich_stressor, aes(x = mass, fill = interaction(as.factor(temp),as.factor(cort), sep="_"))) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 30, color = "black") +
  scale_fill_manual(values = c("28_A" = "red", "23_A" = "blue", "28_B" = "salmon", "23_B" = "lightblue")) +
  labs(x = "Mass", y = "Density", fill = "Temperature ~ CORT") +
  theme_minimal() +
  facet_grid(cort*temp~Day, scales = "free_y")
print(plot_mass)

    #a.2) Latency to move
plot_freeze <- ggplot(guich_stressor, aes(x = log(lat_to_move+1), fill = interaction(as.factor(temp),as.factor(cort), sep="_"))) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 30, color = "black") +
  scale_fill_manual(values = c("28_A" = "red", "23_A" = "blue", "28_B" = "salmon", "23_B" = "lightblue")) +
  labs(x = "Mass", y = "Density", fill = "Temperature ~ CORT") +
  theme_minimal() +
  facet_grid(cort*temp~Day, scales = "free_y")
print(plot_freeze)

# I will both distributions with saphiro.test
mass_normal_test<-by(guich_stressor$mass, interaction (guich_stressor$cort, guich_stressor$temp, guich_stressor$Day), function(x) shapiro.test((x)))
print(mass_normal_test)

freeze_normal_test<-by(guich_stressor$lat_to_move, interaction (guich_stressor$cort, guich_stressor$temp, guich_stressor$Day), function(x) shapiro.test(log(x+1)))
print(freeze_normal_test)
# Once checked the distributions, I will transform lat_to_move with log(x+1) to make it normal
